---
title: "Homework 5"
author: "Wen Dai"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(rvest)
set.seed(123)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```
## Problem 1

For this problem, we are interested in data gathered and made public by _The Washington Post_ on homicides in 50 large U.S. cities. The code chunk below imports and cleans the data.

```{r}
homicide_df = 
  read_csv("data1/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  filter(city_state != "Tulsa, AL") 
```

The resulting dataframe has `r nrow(homicide_df)` entries, on variables that include the victim name, race, age, and sex; the date the homicide was reported; and the location of the homicide. In cleaning, I created a `city_state` variable that includes both city and state, and a `resolution` variable to indicate whether the case was closed by arrest. I also excluded one entry in Tulsa, AL, which is not a major US city and is most likely a data entry error. 

In the next code chunk, I group within cities and summarize to produce the total number of homicides and the number that are solved. 

```{r}
city_homicide_df = 
  homicide_df %>% 
  select(city_state, disposition, resolution) %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolution == "unsolved"))
```

Focusing only on Baltimore, MD, I can use the `prop.test` and `broom::tidy` functions to obtain an estimate and CI of the proportion of unsolved homicides in that city. The table below shows those values.

```{r}
bmore_test = 
  prop.test(
    x = filter(city_homicide_df, city_state == "Baltimore, MD") %>% pull(hom_unsolved),
    n = filter(city_homicide_df, city_state == "Baltimore, MD") %>% pull(hom_total)) 

broom::tidy(bmore_test) %>% 
  knitr::kable(digits = 3)
```

Building on this code, I can use functions in the `purrr` package to obtain estimates and CIs for the proportion of unsolved homicides in each city in my dataset. The code below implements this analysis. 

```{r}
test_results = 
  city_homicide_df %>% 
  mutate(
    prop_tests = map2(hom_unsolved, hom_total, \(x, y) prop.test(x = x, n = y)),
    tidy_tests = map(prop_tests, broom::tidy)) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  mutate(city_state = fct_reorder(city_state, estimate))
```

Finally, I make a plot showing the estimate (and CI) of the proportion of unsolved homicides in each city.

```{r}
test_results %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

This figure suggests a very wide range in the rate at which homicides are solved -- Chicago is noticeably high and, given the narrowness of the CI, likely is the location of many homicides. 

# Problem 2

Part I: Create a tidy data frame containing data from all participants, including the subject ID, arm, and observations over time:

* step 1: Use list.files function to create a dataframe that containing all file names

* step 2: Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe. 

* Step 3: I tidied the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary

```{r}
names=list.files(path = "data", full.names = TRUE) 
data1=sub(".csv","",names)

load_df=function(path)
{
  df= read_csv(path) |> 
  janitor::clean_names() 
}


list_path=
  list(
a="data/con_01.csv",
b="data/con_02.csv",
c="data/con_03.csv", 
d="data/con_04.csv",
e="data/con_05.csv",
f="data/con_06.csv",
g="data/con_07.csv",
h="data/con_08.csv",
i="data/con_09.csv",
g="data/con_10.csv",
k="data/exp_01.csv",
l="data/exp_02.csv",
m="data/exp_03.csv", 
n="data/exp_04.csv",
o="data/exp_05.csv",
p="data/exp_06.csv",
q="data/exp_07.csv",
r="data/exp_08.csv",
s="data/exp_09.csv",
t="data/exp_10.csv"
  )


tidy_df=data.frame(name =data1) |> 
 separate(col =name, into = c("path", "observation1"), sep = "/", remove = FALSE) |> 
  mutate(subject=observation1) |> 
  separate(col =observation1, into=c("group","b"), sep = "_", remove = FALSE) |> 
  select(subject,group) |> 
  mutate(table=map(list_path,load_df)) |>
  unnest(table)

final_tidy_df=tidy_df |>  pivot_longer(week_1:week_8,
               names_to="week",
               names_prefix = "week_",
               values_to = "result") 

final_tidy_df|> knitr::kable(digits = 3)
```

